Fusion Moves for Correlation Clustering

### 2014-11-13 paper/egpaper_for_review.tex
replaced figure with png because there where rendering issues
add new abstract

% Include other packages here, before hyperref.
\usepackage{my_macros}
\usepackage{paralist}
\usepackage{amsthm}
% \usepackage{dirtytalk} fah: my miktex didn't like this; and we don't need it here. 
%\usepackage{framed}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{setspace}
%for tikz
\usepackage{tikz,pgfplots}
\usepackage{pgfplotstable}
\usepackage{filecontents}
%\usepackage{scrextend}
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
\pdfpageattr{/Group <</S /Transparency /I true /CS /DeviceRGB>>}
\usepackage{everypage}
\AddEverypageHook{%
  \makeatletter%
  \special{pdf: put @thispage <</Group << /S /Transparency /I true /CS /DeviceRGB>> >>}%
  \makeatother%
}%

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
  \color{red} \textbf{TODO:}
Correlation clustering, or multicut partitioning, is the NP-hard problem of partitioning an undirected graph or image with positive / attractive and negative / repulsive edge weights such that the sum of cut edge weights is minimized. We here present a move-making heuristic that uses cheaply generated proposal clusterings to iteratively and monotonously improve upon the best previously found clustering. A valid partitioning is maintained at all times, and solutions close to the global optimum are obtained faster than with any published technique.

%We address the problem of partitioning a  graph
%   into a previously unknown number of clusters.
%   Among all partitions, the one with the minimal 
%   sum of of cut edge weights is chosen. 
%   This problem is known as correlation clustering 
%   or multicut.
%   We propose a general framework to find
%   high quality approximate solutions for 
%   this NP-hard problem based on a move making algorithm:
%   We use candidate solutions from a proposal generator
%   to iteratively improve the best observed solution similar
%   to fusion moves.
%   The proposed solver outperforms any other solver
%   w.r.t. to any time performance.
%   The solutions found by this solver are close
%   to global optimal solutions w.r.t. energy
%   and problem specific measurements as VI for
%   image segmentation problems.

\end{abstract}

>>>>

% Include other packages here, before hyperref.
\usepackage{my_macros}
\usepackage{paralist}
\usepackage{amsthm}
% \usepackage{dirtytalk} fah: my miktex didn't like this; and we don't need it here. 
%\usepackage{framed}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{setspace}
%for tikz
\usepackage{tikz,pgfplots}
\usepackage{pgfplotstable}
\usepackage{filecontents}

%\usepackage{scrextend}
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
\pdfpageattr{/Group <</S /Transparency /I true /CS /DeviceRGB>>}
\usepackage{everypage}
\AddEverypageHook{%
  \makeatletter%
  \special{pdf: put @thispage <</Group << /S /Transparency /I true /CS /DeviceRGB>> >>}%
  \makeatother%
}%

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
\input{abstract-new.tex}
%   \color{red} \textbf{TODO:}
% Correlation clustering, or multicut partitioning, is the NP-hard problem of partitioning an undirected graph or image with positive / attractive and negative / repulsive edge weights such that the sum of cut edge weights is minimized. We here present a move-making heuristic that uses cheaply generated proposal clusterings to iteratively and monotonously improve upon the best previously found clustering. A valid partitioning is maintained at all times, and solutions close to the global optimum are obtained faster than with any published technique. 
%    
%We address the problem of partitioning a  graph
%   into a previously unknown number of clusters.
%   Among all partitions, the one with the minimal 
%   sum of of cut edge weights is chosen. 
%   This problem is known as correlation clustering 
%   or multicut.
%   We propose a general framework to find
%   high quality approximate solutions for 
%   this NP-hard problem based on a move making algorithm:
%   We use candidate solutions from a proposal generator
%   to iteratively improve the best observed solution similar
%   to fusion moves.
%   The proposed solver outperforms any other solver
%   w.r.t. to any time performance.
%   The solutions found by this solver are close
%   to global optimal solutions w.r.t. energy
%   and problem specific measurements as VI for
%   image segmentation problems.
%
\end{abstract}
\vspace{-0.5cm}
